Notes for Week 6/13/19 - 6/18/19

### 2019-06-19 notes/weekly_notes/6.18.19.NotesForWeek.tex
added weekly notes

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}

@@

\begin{document}
\title{Notes for Week 6/9/19 - 6/11/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $f,g$ be $L^2$ density functions supported on the $d$-dimensional unit cube $[0,1]^d$, meaning
\begin{equation*}
\int_{[0,1]^d} f(x)^2 dx, \int_{[0,1]^d} g(x)^2 dx < \infty, \quad \text{and} \quad \int_{[0,1]^d} f(x) dx, \int_{[0,1]^d} g(x) dx = 1.
\end{equation*}
with $f$,$g$ bounded away from $0$, $f(x), g(x) > p_{\min}$ for all $x \in [0,1]^d$.

@@

For a given function class $\Hclass$, some $\epsilon > 0$, and test function $\phi$ a Borel measurable function of the data with range $\set{0,1}$, we evaluate the quality of the test using \emph{worst-case risk}
\begin{equation*}
R_{\epsilon}^{(t)}(\phi; \Hclass) = \sup_{f \in \Hclass} \Ebb_{f,f}^{(t)}(\phi) + \sup_{ \substack{f,g \in \Hclass \\ \delta(f,g) \geq \epsilon } } \Ebb_{f,g}^{(t)}(1 - \phi)
\end{equation*} 
where 
\begin{equation*}
\delta^2(f,g) = \int_{\D} (f - g)^2 dx.
\end{equation*}
We will consider those density functions which belong to $\mathcal{H} := \mathcal{H}_{1}^d(L)$, the $d$-dimensional Lipschitz ball with norm $L$. Formally, a function $f \in \mathcal{H}$ if for all $x,y \in [0,1]^d$, $\abs{f(x) - f(y)} \leq L \norm{x - y}$.\footnote{Note that the Lipschitz requirement, along with the restriction that $f$ be a density function over a bounded domain, imply that $f$ has finite $L^2$ norm.}

\section{Sieve-based test.}

For a radius $r > 0$ to be determined later, the $r$-neighborhood graph $G = (V,E)$ consists of vertices $V = [n]$ corresponding to the $n$ data points, and edges $E = \set{(u,v): \norm{x_u - x_v} \leq r}$. Write $D$ for the incidence matrix of this graph, and $L = D^T D$ for the graph Laplacian. Denote the singular value decomposition of $D$ by $D = U \Lambda^{1/2} V^T$, where $U$ and $V$ are orthonormal matrices and $\Lambda$ is a diagonal matrix with entries $0 = \lambda_1 \leq \lambda_2 \leq \lambda_3 \leq \ldots \leq \lambda_n$, so that $L = V \Lambda V^T$. For $k = 1,\ldots,n$, write $V_k = (v_1 \ldots v_k)$ for the $n \times k$ matrix containing the first $k$ columns of $V$--that is, the first $k$ eigenvectors of $L$. Our first test statistic will be as follows:

\begin{equation}
\label{eqn: laplacian_eigenmaps_statistic}
T_{LE}^{(k)} := \sup_{\substack{\theta \in \mathrm{col}(V_k), \\ \norm{\theta} = 1} } \dotp{\theta}{\ell}^2 = \ell^T V_k V_k^T \ell.
\end{equation}

\subsection{Assumptions}
The following are statements I wish to hold in order for the later theory to follow, but I cannot yet prove:
\begin{enumerate}
	\item There exists a constant $c_1 > 0$ -- which may depend on dimension $d$ but not on $n$ --  such that for all $h \in 1, \ldots,k$ and all $i = 1,\ldots,n$, 
	\begin{equation}
	\label{eqn: asmp_1}
	\abs{v_{hi}} \leq \frac{c}{\sqrt{n}}
	\end{equation}
\end{enumerate}

If $v_k$ were eigenvectors of the grid--rather than of the neighborhood graph--the first item would hold with $c = 2^{d/2}$.

\subsection{Main result.}
Let $d = 3,4$, choose $r = c(\log(n)/n)^{1/d}$ to satisfy the condition of Lemma \ref{lem: approximation_error}, and let $k = n^{2d/(d + 4)}$. Let 
\begin{equation*}
\phi_{LE} =
\begin{cases}
1,~ & \text{if}~ T_{LE}^{(k)} \geq k + a\sqrt{2k + c^4\left(k + \frac{k^2}{n}\right)} \\
0,~ & \text{otherwise}.
\end{cases}
\end{equation*}
The following theorem holds.
\begin{theorem}
	There exists some number $c > 0$ constant in sample size $n$ such that for any $\epsilon \geq c n^{-2/(4 + d)}$, we have
	\begin{equation*}
	R_{\epsilon}^{(t)}(\phi_{LE}; \Hclass_1^{d}(L)) \leq \frac{1}{a^2}.
	\end{equation*}
	when $d = 3$ or $4$. 
\end{theorem}
\begin{proof}

\end{proof}

\subsection{Type I error}

Under the null hypothesis, $\ell$ consists of $n$ independent and identically distributed Rademacher random variables. Using this fact, we can bound the first two moments of $T_{LE}$ under the null hypothesis.

\begin{lemma}
	If $f = g$, then
	\begin{equation}
	\Ebb(T_{LE}^{(k)}) = k
	\end{equation}
	and
	\begin{equation}
	\label{eqn: variance_noise_typeI}
	\Var(T_{LE}^{(k)}) \leq 2k + c_1^4\left(k + \frac{2k^2}{n}\right)
	\end{equation}
\end{lemma}
\begin{proof}
	Taking the expectation first, we have
	\begin{align*}
	\Ebb(T_{LE}^{(k)}) & = \sum_{j = 1}^{k} \Ebb((\ell^T v_j)^2) \\
	& = \sum_{j = 1}^{k} \sum_{i = 1}^{n} \sum_{i' = 1}^{n} \Ebb(\ell_i \ell_{i'}) v_{ji} v_{ji'} \\
	& =  \sum_{j = 1}^{k} \sum_{i = 1}^{n} v_{ji}^2 = k.
	\end{align*}

	We defer the proof of \eqref{eqn: variance_noise_typeI} until the following subsection, where we show it in greater generality.
\end{proof}

\subsection{Type II error.}

Write $\ell =: \thetast + w$, where $\thetast = (\thetast_i)$ is defined by
\begin{equation*}
\thetast_i = \frac{f(x_i) - g(x_i)}{f(x_i) + g(x_i)}
\end{equation*}
and $w = (w_i)$ therefore consists of $n$ independent (although not identically distributed) zero-mean noise terms. We expand
\begin{equation}
\label{eqn: LE_expansion}
\ell^T V_k V_k^T \ell = (\thetast)^T V_k V_k^T \thetast + w^T V_k V_k w + 2 w^T V_k V_k^T \thetast,
\end{equation}
and focus at first our attention on the second term in \eqref{eqn: LE_expansion}.

\begin{lemma}
	Assuming \eqref{eqn: asmp_1} holds,
	\begin{equation}
	\label{eqn: expectation_noise_typeII}
	\Ebb \left( w^T V_k V_k w\right) \geq k - \frac{kc_1^2 \delta^2(f,g)}{p_{\min}^2}
	\end{equation}
	and
	\begin{equation}
	\label{eqn: variance_noise}
	\Var(T_{LE}^{(k)}) \leq 2k + c_1^4\left(k + \frac{2k^2}{n}\right)
	\end{equation}
\end{lemma}
\begin{proof}
	We note that, conditional on $X$,
	\begin{equation*}
	w_i = 
	\begin{cases}
	2\frac{g(x_i)}{f(x_i) + g(x_i)},~ & \text{with probability}~ \frac{f(x_i)}{f(x_i) + g(x_i)} \\
	-2\frac{f(x_i)}{f(x_i) + g(x_i)},~ & \text{with probability}~ \frac{g(x_i)}{f(x_i) + g(x_i)}
	\end{cases}
	\end{equation*}

	We first show \eqref{eqn: expectation_noise_typeII}. Expanding the quadratic form as a double sum, and using the law of iterated expectation, we have
	\begin{align}
	\label{eqn: expectation_noise_typeII_1}
	\Ebb \left( w^T V_k V_k w\right) & = \sum_{h = 1}^{k} \sum_{i = 1}^{n} \sum_{j = 1}^n \Ebb \bigl(w_i w_j v_{hi} v_{hj} \bigr) \nonumber \\
	& = \sum_{h = 1}^{k} \sum_{i = 1}^{n} \sum_{j = 1}^n \Ebb \biggl( \Ebb\Bigl(w_i w_j \bigl\vert x_i, x_j\Bigr) v_{hi} v_{hj}\biggr) \nonumber \\
	& = \sum_{h = 1}^{k} \sum_{i = 1}^{n} \Ebb \biggl( \Ebb\Bigl(w_i^2 \bigl\vert x_i\Bigr) v_{hi}^2\biggr).
	\end{align}
	The conditional expectation $\Ebb\Bigl(w_i^2 \bigl\vert x_i\Bigr)$ can be directly computed,
	\begin{align*}
	\Ebb\Bigl(w_i^2 \bigl\vert x_i\Bigr) & = 4\left(\frac{g(x_i)}{f(x_i) + g(x_i)}\right)^2 \frac{f(x_i)}{f(x_i) + g(x_i)} + 4\left(\frac{f(x_i)}{f(x_i) + g(x_i)}\right)^2 \frac{g(x_i)}{f(x_i) + g(x_i)} \\
	& = 4 \frac{f(x_i)g(x_i)(f(x_i) + g(x_i))}{(f(x_i) + g(x_i))^3} \\
	& = 4 \frac{f(x_i)g(x_i)}{(f(x_i) + g(x_i))^2}.
	\end{align*}
	and plugging this back into \eqref{eqn: expectation_noise_typeII_1}, we obtain
	\begin{align*}
	\Ebb \left( w^T V_k V_k w\right) & = \sum_{h = 1}^{k} \sum_{i = 1}^{n} \Ebb \left(4 \frac{f(x_i) g(x_i)}{(f(x_i) + g(x_i))^2} v_{hi}^2\right) \\
	& = \sum_{h = 1}^{k} \sum_{i = 1}^{n} \Ebb \left(v_{hi}^2 \left(1 - \left(\frac{f(x_i) - g(x_i)}{f(x_i) + g(x_i)} \right)^2 \right)\right) \\
	& \geq k - \frac{c^2}{n}\sum_{h = 1}^{k} \sum_{i = 1}^{n} \Ebb \left(\frac{f(x_i) - g(x_i)}{f(x_i) + g(x_i)} \right)^2 \\
	& \geq k - \frac{kc_1^2 \delta^2(f,g)}{p_{\min}^2}
	\end{align*}
	and \eqref{eqn: expectation_noise_typeII} is shown.

	We now show \eqref{eqn: variance_noise}. It will be helpful to note that for all $i,i',j,j' \in [n]$,
	\begin{equation*}
	\mathrm{Cov}(w_iw_j, w_{i'}w_{j'} | X) = 
	\begin{cases}
	0, & \text{if}~ \set{i,i',j,j'}~ \textrm{has four distinct elements} \\
	0, & \text{if}~ \set{i,i',j,j'}~ \textrm{has three distinct elements} \\
	0, & \text{if}~ \set{i,i',j,j'}~ \textrm{has two distinct elements and}~ i = j \\
	\Ebb(w_i^2|X) \Ebb(w_j^2|X), & \text{if}~ \set{i,i',j,j'}~ \textrm{has two distinct elements and}~ i \neq j \\
	\Var(w_i^4|X), & \text{if}~ \set{i,i',j,j'}~ \textrm{has one distinct element.}
	\end{cases}
	\end{equation*}
	and additionally
	\begin{equation*}
	\Ebb(w_iw_j|X) =
	\begin{cases}
	0, & \text{if}~ i \neq j \\
	E(w_i^2|X), & \text{if}~ i = j.
	\end{cases}
	\end{equation*}
	Then, by the law of total covariance,
	\begin{align*}
	\mathrm{Var}(w^T V_k V_k^T w) & = \sum_{h,h' = 1}^{k} \sum_{i,i' = 1}^{n} \sum_{j,j' = 1}^{n} \mathrm{Cov} \bigl(w_iw_jv_{hi} v_{hj}, w_{i'}w_{j'}v_{h'i'} v_{h'j'}\bigr) \\
	& = \sum_{h,h' = 1}^{k} \sum_{i,i' = 1}^{n} \sum_{j,j' = 1}^{n} \Ebb \Bigl(  v_{hi} v_{hj} v_{h'i'} v_{h'j'} \mathrm{Cov} \bigl(w_iw_j, w_{i'}w_{j'} |X\bigr)\Bigr) + \\
	& \quad \quad \mathrm{Cov} \Bigl( v_{hi}v_{hj} \Ebb(w_iw_j|X), v_{h'i'}v_{h'j'} \Ebb(w_i'w_j'|X)  \Bigr) \\
	& = 2 \sum_{h,h' = 1}^{k} \sum_{i \neq j}^{n} \Ebb\Bigl( v_{hi} v_{hj} v_{h'i} v_{h'j} \Ebb(w_i^2|X) \Ebb(w_j^2|X) \Bigr) + \\
	& \quad \quad \sum_{h,h' = 1}^{k} \sum_{i = 1}^{n} \Ebb \left(v_{hi}^2 v_{h'i}^2 \Var(w_i^4|X)\right) +  \\
	& \quad \quad \quad \sum_{h,h' = 1}^{k} \sum_{i,i' = 1}^{n} \mathrm{Cov} \bigl( v_{hi} ^2 \Ebb(w_i^2|X), v_{h'i'}^2 \Ebb(w_{i'}^2|X)\bigr)
	\end{align*}
	Then, using the upper bound $\Ebb(w_i^2|X),\Ebb(w_j^2|X) \leq 1$, we can bound the first term
	\begin{align*}
	\sum_{h,h' = 1}^{k} \sum_{i \neq j}^{n} \Ebb\Bigl( v_{hi} v_{hj} v_{h'i} v_{h'j} \Ebb(w_i^2|X) \Ebb(w_j^2|X) \Bigr) & \leq \sum_{h,h' = 1}^{k} \sum_{i \neq j}^{n} \Ebb\Bigl( v_{hi} v_{hj} v_{h'i} v_{h'j} \Bigr) \\
	& \leq \sum_{h,h' = 1}^{k} \Ebb\Bigl( \sum_{i = 1}^{n}v_{h'i} v_{hi} \sum_{j = 1}^{n} v_{h'j} v_{hj} \Bigr) \\
	& = \sum_{h = 1}^{k} 1 = k.
	\end{align*}

	To bound the second term, we note that $\Var(w_i^4|X) \leq 1$, and along with \eqref{eqn: asmp_1} this yields
	\begin{align*}
	\sum_{h,h' = 1}^{k} \sum_{i = 1}^{n} \Ebb \left(v_{hi}^2 v_{h'i}^2 \Var(w_i^4|X)\right) \leq \sum_{h,h' = 1}^{n} \sum_{i = 1}^{n} \frac{c_1^4}{n^2} = \frac{c_1^4k^2}{n}.
	\end{align*}

	Finally, to bound the third term we note that if $h \neq h'$ and $i \neq i'$,
	$\mathrm{Cov} \bigl( v_{hi} ^2 \Ebb(w_i^2|X), v_{h'i'}^2 \Ebb(w_{i'}^2|X)\bigr) = 0$. Therefore,
	\begin{align*}
	\sum_{h,h' = 1}^{k} \sum_{i,i' = 1}^{n} \mathrm{Cov} \bigl( v_{hi} ^2 \Ebb(w_i^2|X), v_{h'i'}^2 \Ebb(w_{i'}^2|X)\bigr) & = \sum_{h = 1}^{k} \sum_{i = 1}^{n} \sum_{j = 1}^{n} \mathrm{Cov} \bigl( v_{hi} ^2 \Ebb(w_i^2|X), v_{hi'}^2 \Ebb(w_{i'}^2|X)\bigr) + \\
	& \quad \quad \sum_{h \neq h'}^{k} \sum_{i = 1}^{n} \mathrm{Cov} \bigl( v_{hi} ^2 \Ebb(w_i^2|X), v_{h'i}^2 \Ebb(w_{i}^2|X)\bigr) \\
	& \leq \sum_{h = 1}^{k} \sum_{i = 1}^{n} \sum_{j = 1}^{n} \frac{c_1^4}{n^2} + \sum_{h \neq h'}^{k} \sum_{i = 1}^{n} \frac{c_1^4}{n^2} \\
	& = c_1^4 k + c_1^4 \frac{k^2}{n},
	\end{align*}
	and putting the pieces together yields \eqref{eqn: variance_noise}.
\end{proof}

Now, we turn our attention to the third term of \eqref{eqn: LE_expansion}.
\begin{lemma}
	\begin{equation}
	\Ebb(w^T V_k V_k^T \thetast) = 0
	\end{equation}
	and assuming \eqref{eqn: asmp_1} holds,
	\begin{equation*}
	\Var(w^T V_k V_k^T \thetast) \leq k \frac{c_1^2 \delta^2(f,g)}{p_{\min}^2}
	\end{equation*}
\end{lemma}

Finally, we examine the first term in \eqref{eqn: LE_expansion}. We will need the following result.
\begin{lemma}
	For any $0 < \delta < 1$, there exists a number $c_2 > 0$ depending only on $d$ and $\delta$ such that, if $r \geq c_2(\log n/n)^{1/d}$, then
	\begin{equation*}
	\norm{D \thetast}^2 \leq \frac{16 L^4}{p_{\min}^2} n^2 r^{d + 2}
	\end{equation*}
	and
	\begin{equation*}
	\lambda_k \geq \frac{4 k^{2/d}}{\pi^2 n^{2/d}}
	\end{equation*}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{lemma}
	\label{lem: approximation_error}
	For any $\delta > 0$, there exists a number $c_2 > 0$ constant in sample size such that if $r \geq c_2 (\log n / n)^{1/d}$,
	\begin{equation*}
	(\thetast)^T V_k V_k^T \thetast \geq n (\delta(f,g))^2 - \frac{n^2r^{d + 2} n^{2/d}}{k^{2/d}}
	\end{equation*}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{proof}
	Letting $z = D \thetast$, we have
	\begin{align*}
	(\thetast)^T V_k V_k^T \thetast & = \norm{\thetast}^2 - (\thetast)^T \left(I - V_k V_k^T \right) \thetast \\
	& = \norm{\thetast}^2- z^T (D^{\dagger})^T (I - V_k V_k^T) D^{\dagger} z \\
	& \geq \norm{\thetast}^2 - z^T z \lambda_{\max} \Bigl((D^{\dagger})^T (I - V_k V_k^T) D^{\dagger} \Bigr) \\
	& \geq \norm{\thetast}^2 - \frac{z^T z}{\lambda_{k}}
	\end{align*}
	Examining $\norm{\thetast}^2$, we have that
	\begin{equation*}
	\Ebb(\norm{\thetast}^2) = n \delta^2(f,g) \quad \text{and} \quad \Var(\norm{\thetast}^2) \leq n \delta^2(f,g)
	\end{equation*}
	Turning to the second term, we have given our choice of $r$, along with the fact $f - g \in \mathcal{H}_1^{d}(2L)$,
	\begin{equation*}
	z^T z = \norm{D \thetast}^2 \leq \frac{16 L^4}{p_{\min}^2} n^2 r^{d + 2}
	\end{equation*}
	and additionally
	\begin{equation*}
	\lambda_k \geq \frac{4 k^{2/d}}{\pi^2 n^{2/d}},
	\end{equation*}
	each with probability $1 - \delta$.
\end{proof}

>>>>

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\dxpr}{\,dx'}
\newcommand{\dypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}

@@

\begin{document}
\title{Notes for Week 6/13/19 - 6/18/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $f,g$ be $L^2$ density functions supported on the $d$-dimensional unit cube $[0,1]^d$, meaning
\begin{equation*}
\int_{[0,1]^d} f(x)^2 dx, \int_{[0,1]^d} g(x)^2 dx < \infty, \quad \text{and} \quad \int_{[0,1]^d} f(x) dx, \int_{[0,1]^d} g(x) dx = 1.
\end{equation*}
with $f$,$g$ bounded above and below, $0 < p_{\min} < f(x), g(x) < p_{\max} < \infty$ for all $x \in [0,1]^d$.

@@

For a given function class $\Hclass$, some $\epsilon > 0$, and test function $\phi$ a Borel measurable function of the data with range $\set{0,1}$, we evaluate the quality of the test using \emph{worst-case risk}
\begin{equation*}
R_{\epsilon}^{(t)}(\phi; \Hclass) = \sup_{f \in \Hclass} \Ebb_{f,f}^{(t)}(\phi) + \sup_{ \substack{f,g \in \Hclass \\ \delta(f,g) \geq \epsilon } } \Ebb_{f,g}^{(t)}(1 - \phi)
\end{equation*} 
where 
\begin{equation*}
\delta^2(f,g) = \int_{\D} (f - g)^2 dx.
\end{equation*}
We will consider the function class $\mathcal{H} := \mathcal{H}_{1}^d(L)$, the $d$-dimensional Lipschitz ball with norm $L$. Formally, a function $f \in \mathcal{H}$ if for all $x,y \in [0,1]^d$, $\abs{f(x) - f(y)} \leq L \norm{x - y}$.\footnote{Note that the Lipschitz requirement, along with the restriction that $f$ be a density function over a bounded domain, imply that $f$ has finite $L^2$ norm.}

\section{Test Statistic}

Let $r > 0$ be a bandwidth parameter, let $\eta_r: \mathcal{X} \times \mathcal{X} \to [0,\infty)$ be a Mercer kernel given by
\begin{equation*}
\eta_r(x,y) =
\begin{cases}
1, \quad & \textrm{$\norm{x - y} \leq r$} \\
0, \quad & \textrm{$\norm{x - y} > r$},
\end{cases}
\end{equation*}
and let $\widetilde{A}$ be an $n \times n$ matrix with entries $\widetilde{A}_{ij} = n^{-1}\eta(x_i,x_j)$. We obtain $A$ from $\widetilde{A}$ be setting all diagonal entries of $\widetilde{A}$ to be zero. Our test statistic is then
\begin{equation*}
T_{\eta} := \ell^T A \ell.
\end{equation*}

\section{Theory}

\begin{theorem}

\end{theorem}

\section{Supporting Theory}

We begin by recalling Chebyshev's inequality, which we will use to bound deviations of $T_{\eta}$ from its expectation.
\begin{lemma}[Chebyshev]
	\label{lem: chebyshev}
	Let $X$ be a random variable with $\Ebb X < \infty$ and $0 < \Var(X) < \infty$. Then,
	\begin{equation*}
	\Pbb(\abs{X - \Ebb X} \geq a) \leq \frac{\Var(X)}{a^2}.
	\end{equation*}
\end{lemma}

In order to employ Lemma \ref{lem: chebyshev}, we must bound the expectation and variance of $T_{\eta}$ under the null and alternative hypotheses. We begin with the expectation $\Ebb T_{\eta}$. 
\begin{lemma}
	\label{lem: mmd_expectation}
	Under the null hypothesis $h = g$, for any $h, g \in \mathcal{H}_{1}^{d}(L)$,
	\begin{equation*}
	\Ebb T_{\eta} = 0.
	\end{equation*}

	Under the alternative hypothesis $h \neq g$, for any $h, g \in \mathcal{H}_{1}^{d}(L)$, 
	\begin{equation*}
	\Ebb T_{\eta} \geq \frac{(n - 1)p_{\min}^2}{ p_{\max}^2} \left(\delta^2(f,g)\frac{r^d}{2^d} - L\delta(f,g)r^{d + 1}\right)
	\end{equation*}
\end{lemma}
\begin{proof}
	Let $\thetast$ be a vector in $\Reals^{n}$, with entries $ \thetast_i = \Ebb(\ell_i|x_i)$. Letting $w = \ell - \thetast$, we note that conditional on $X$, the noise component $w$ consists of $n$ independent and zero mean terms.

	We expand the test statistic
	\begin{equation*}
	T_{\eta} = (\thetast)^T A \thetast + w^T A w + 2 w^T A \thetast
	\end{equation*}
	and note that by the law of iterated expectation, 
	\begin{equation*}
	\Ebb(T_{\eta}) = \Ebb(T_{\eta}|X) = \Ebb\left( (\thetast)^T A \thetast \right)
	\end{equation*}

	Now, let $X$ and $Y$ be independent random variables with distribution $\mu$, and let $\Delta(x) := f(x) - g(x)$. By the linearity of expectation,
	\begin{align*}
	\Ebb (\thetast)^T A \thetast & = \sum_{i \neq j = 1}^{n} \Ebb( \thetast_i \thetast_j A_{ij}) \\
	& = (n - 1) \Ebb \bigl(\thetast_1 \thetast_2 \eta_r(x_1, x_2) \bigr) \\
	& \geq \frac{4(n - 1)}{p_{\max}^2} \Ebb(\Delta(x) \Delta(y) \eta_r(X,Y))
	\end{align*}

	We can lower bound $\Ebb(\Delta(x) \Delta(y) \eta_r(X,Y))$ by $\delta^2(f,g)$, minus a remainder term, as follows
	\begin{align*}
	\Ebb(\Delta(x) \Delta(y) \eta_r(X,Y)) & = \iint \Delta(x) \Delta(y) \eta_r(x,y) d\mu(x) d\mu(x) \\
	& \geq \frac{p_{\min}^2}{4} \iint \Delta(x) \Delta(y) \eta_r(x,y) dx dy \\
	& \geq \frac{p_{\min}^2}{4} \left( \iint \Delta^2(x) \eta_r(x,y) dx dy - \iint \abs{\Delta(x)} \abs{\Delta(x) - \Delta(y)} \eta(x,y) dx dy \right)
	\end{align*}
	To lower bound the first term, observe that for any $x \in [0,1]^d$,
	\begin{equation*}
	\int_{[0,1]^d} \eta_r(x,y) dx \geq \frac{r^d}{2^d}
	\end{equation*}
	and therefore
	\begin{equation*}
	\iint \Delta^2(x) \eta_r(x,y) dx dy \geq \frac{r^d}{2^d} \int_{[0,1]^d} \Delta^2(x) dx \geq \frac{r^d}{2^d} \delta^2(f,g).
	\end{equation*}

	To upper bound the remainder term, observe that $\Delta \in \mathcal{H}_{1}^{d}(2L)$. Using this fact, we obtain the upper bound
	\begin{align*}
	\iint \abs{\Delta(x)} \abs{\Delta(x) - \Delta(y)} \eta(x,y) dx dy & \leq : \iint \abs{\Delta(x)} \norm{x - y} \eta(x,y) dx dy \\
	& \leq L r^{d + 1} \int_{[0,1]^d} \abs{\Delta(x)} dx \\
	& \leq L r^{d + 1} \delta(f,g).
	\end{align*}
	where the last inequality follows from Jensen's inequality.
\end{proof}

\begin{lemma}
	\label{lem: var_mmd}
	For any $h,g \in \mathcal{H}_1^{d}(L)$,
	\begin{equation*}
	\Var(T_{\eta}) \leq 2n \frac{p_{\max}^2}{p_{\min}^2} r^d \left(r^d \delta^2(f,g) + Lr^{d+1}\delta(f,g)\right) + 2r^d
	\end{equation*}
\end{lemma}
\begin{proof}
	We begin by computing the second moment $\Ebb T_{\eta}^2$. Expanding the quadratic form, we obtain
	\begin{align}
	\Ebb T_{\eta}^2 =  \sum_{i,i' = 1}^{n} \sum_{j,j' = 1}^{n} \Ebb(\ell_i \ell_{i'} \ell_{j} \ell_{j'} A_{ii'} A_{jj'})
	\end{align}

	We next compute this expectation, based on the number of distinct indices $i,i',j,j'$. Let $X, X', Y, Y'$ be four independent random variables, each with distribution $\mu$, and write $\widetilde{\Delta} := 2 \Delta / \mu$.  Then, applying the law of conditional expectation, we obtain
	\begin{equation*}
	n^2 \Ebb(\ell_i \ell_{i'} \ell_{j} \ell_{j'} A_{ii'} A_{jj'}) = 
	\begin{cases}
	\Ebb(\widetilde{\Delta}(X) \wt{\Delta}(X') \eta_r(X,X'))^2, \quad & \textrm{if}~ \set{i,i',j,j'} ~\textrm{contains four distinct elements}, \\
	\Ebb(\widetilde{\Delta}(X') \wt{\Delta}(Y') \eta_r(X,X') \eta_r(X,Y')), \quad & \textrm{if}~ \set{i,i',j,j'} ~\textrm{contains three distinct elements and}~ i = j, \\
	\Ebb\biggl(\eta_r(X,Y)^2\biggr), \quad  & \textrm{if}~ \set{i,i',j,j'} ~\textrm{contains two distinct elements and}~ i = j. \\
	0, \quad & \textrm{if}~ i = i' ~\textrm{or}~ j = j'.
	\end{cases}
	\end{equation*}
	and as a result we obtain
	\begin{align}
	\label{eqn: var_mmd_1}
	n^2 \Ebb T_{\eta}^2 = & n(n-1)(n-2)(n-3)\Ebb\biggl(\widetilde{\Delta}(X) \wt{\Delta}(X') \eta_r(X,X')\biggr) + \nonumber \\
	& \quad 2n(n-1)(n-2) \Ebb \biggl(\widetilde{\Delta}(X') \wt{\Delta}(Y') \eta_r(X,X') \eta_r(X,Y') \biggr) + \nonumber \\
	& \quad \quad 2n(n-1) \Ebb\biggl(\eta_r(X,Y)^2\biggr).
	\end{align}

	The first term -- covering the case when $\set{i,i',j,j'}$ contains four distinct elements --  will be canceled out by the mean, as we will see, and we do not simplify it further.

	The second term we upper bound by methods similar to those used to obtain the upper bound in Lemma \ref{lem: mmd_expectation}. We will need the following upper bound,
	\begin{align*}
	\int \eta(x,x') \eta(x,y') \dx & \leq r^d \1(\norm{x' - y'} \leq 2r) \\
	& = r^d \eta_{2r}(x',y').
	\end{align*}
	We proceed,
	\begin{align}
	\label{eqn: var_mmd_2}
	\Ebb \biggl(\widetilde{\Delta}(X') \wt{\Delta}(Y') \eta_r(X,X') \eta_r(X,Y') \biggr) & \leq \frac{p_{\max}^2}{p_{\min}^2} \iiint \Delta(x') \Delta(y') \eta(x,x') \eta(x,y') \dx \dypr \dxpr \nonumber\\
	& \leq \frac{p_{\max}^2}{p_{\min}^2} r^d \iint \Delta(x') \Delta(y') \eta_{2r}(x',y') \dypr \dxpr \nonumber \\
	& \leq \frac{p_{\max}^2}{p_{\min}^2} r^d \left(r^d \delta^2(f,g) + Lr^{d+1}\delta(f,g)\right).
	\end{align}

	The following upper bound on the third term is a straightforward consequence of the fact $\eta_r^2 = \eta_r$, and therefore
	\begin{equation}
	\label{eqn: var_mmd_3}
	\Ebb(\eta_r(X,Y)^2) = \Ebb(\eta_r(X,Y)) = r^d. 
	\end{equation}

	Finally, we have that
	\begin{equation}
	\label{eqn: var_mmd_4}
	n^2 \Ebb(T_{\eta}^2) = \left(n(n-1) \Ebb(\widetilde{\Delta}(X) \wt{\Delta}(X') \eta_r) \right)^2 .
	\end{equation}

	Combining \eqref{eqn: var_mmd_1}-\eqref{eqn: var_mmd_4}, we obtain
	\begin{equation*}
	\Var(T_\eta) \leq 2n \frac{p_{\max}^2}{p_{\min}^2} r^d \left(r^d \delta^2(f,g) + Lr^{d+1}\delta(f,g)\right) + 2r^d.
	\end{equation*}
\end{proof}
